### 2022-11-29 dissertation/chapters/03-heuristics.tex
🚧 (final-review): Chapter 8 WIP

The update step for \acs{GD} by means of \acs{BP} can be formulated as is shown in Equations~\eqref{eq:heuristics:gd:update_step_part_1}-\eqref{eq:heuristics:gd:update_step_part_4}. The general weight update step is given as

>>>>

The update step for \acs{GD} by means of \acs{BP} can be formulated as is shown in Equations~\eqref{eq:heuristics:gd:update_step_part_1} to \eqref{eq:heuristics:gd:update_step_part_4}. The general weight update step is given as

### 2022-11-29 dissertation/chapters/07-methodology.tex
🚧 (final-review): Chapter 8 WIP

This section provides the stopping conditions that are used during the empirical process. For this dissertation, the \textit{maximum epoch} stopping condition is used, where a fixed, maximum number of training steps and epochs are executed and training is not haulted until the maximum number of epochs have been reached. \acp{FFNN} are trained for a maximum of 30 epochs. Early stopping is a technique where training is stopped when the \index{heuristic}heuristic is not able to improve the performance of the \acs{FFNN} for a number of steps. If the performance has not improved, the training is halted and the last known best model weights are restored. Early stopping is not implemented for the empirical process in this dissertation. This design decision is made so that the behaviour of the \acs{BHH} can be studied beyond the point of optimal results.

>>>>

This section provides the stopping conditions that are used during the empirical process. For this dissertation, the \textit{maximum epoch} stopping condition is used, where a fixed, maximum number of training steps and epochs are executed and training is not halted until the maximum number of epochs have been reached. \acp{FFNN} are trained for a maximum of 30 epochs. Early stopping is a technique where training is stopped when the \index{heuristic}heuristic is not able to improve the performance of the \acs{FFNN} for a number of steps. If the performance has not improved, the training is halted and the last known best model weights are restored. Early stopping is not implemented for the empirical process in this dissertation. This design decision is made so that the behaviour of the \acs{BHH} can be studied beyond the point of optimal results.
